Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-05-29 manuscripts/manuscript.Rmd
updated packrat configuration

layout: preprint, 11pt

bibliography: components/references.bib
csl: components/ecology.csl

@@

```{r caching, include=FALSE, output="hide"}
library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

@@

```{r libraries, output="hide", include=FALSE, cache=FALSE}
rm(list=ls())
library("pdgControl")
library("reshape2")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
theme_set(theme_tufte())
```

@@

```{r parallel, include=FALSE}
require(snowfall)
sfInit(cpu=4, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````

>>>>

layout: preprint

bibliography: components/references.bib
csl: components/ecology.csl
documentclass: components/elsarticle

@@

```{r dependencies, include=FALSE}
source("components/install.R")
```

```{r caching, include=FALSE}
library("methods")
library("knitr")
basename <- "manuscript"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

@@

```{r libraries, include=FALSE, cache=FALSE}
rm(list=ls())
library("rmarkdown")
library("pdgControl")
library("reshape2")
library("ggplot2")
library("data.table")
library("pander")
library("cboettigR")
library("ggthemes")
library("snowfall")
theme_set(theme_tufte())
ncpu = 1
```

@@

```{r parallel, include=FALSE}
sfInit(cpu=ncpu, parallel=T)
sfLibrary(pdgControl)
sfExportAll()
````
